Pillar 1 - Sequential Pattern Mining

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
relocate files to Output folder

```{r library, message = F}
#detach(package:tm, unload=TRUE) #there is overlap with tm package in inspect()

library(tidyverse)
library(arules)
library(arulesSequences)

library(rlang)

library(ggplot2)
```

# Setup
load previous data and create function to find courses
```{r loading data}
load("data_pillar_1.RDATA")

find_course <- function(code){ #can be modified to accept other data that is not d_transcript
  c = code
  x <- d_transcript %>%
    filter(`Course Code`== c)

  return(x$`Course Title`[1])
}

```
#Simple Rule Mining
##Data Exploration of Transcripts
```{r}
exploration <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG"~ "-1", #"0,0", #maybe we could just remove these from the analysis and treat them separately?
                           T~Grade),
         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
         Grade = as.numeric(Grade))%>%
  filter(!is.na(Grade)) %>%
  filter(Grade != -1) #remove NG

>>>>

```{r library, message = F}
library(tidyverse)

library(arules)
library(arulesSequences)
library(rlang)
```

# Setup
load previous data and create function to find courses
```{r loading data}
load("data_pillar_1.RDATA")
```

Function that returns title of a course given its code.
```{r}
find_course <- function(code){

  dataset <- d_transcript %>%
    filter(`Course ID`== code)

  title <- dataset$`Course Title`[1]

  return(title)

}
```

#Simple Rule Mining
##Data Exploration of Transcripts
```{r}
exploration <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG"~ "-1", #"0,0", #maybe we could just remove these from the analysis and treat them separately?
                           T~Grade),
         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
         Grade = as.numeric(Grade))%>%
  filter(!is.na(Grade)) %>%
  filter(Grade != -1) #remove NG
